Evolving New State-of-the-Art for Voronoi Diagram and Distance Transform From JFA Using AutoML

### 2020-09-19 paper/main.tex
"proposed method" section (1/5)

Based on this research and findings, several efficient GPU-based algorithms
which are either work optimal or time optimal have been proposed including SKW
\cite{schneider2009gpu}, PBA \cite{cao2010parallel}, FastGPU \cite{de2017fast},
Honda's algorithm \cite{honda2017simple} and WTO \cite{manduhu2019work}.
% XXX
The main question that needs to be addressed is whether JFA has potential for
improvement. We found some benefits for specific data by adding random noise and
adjusting the phase size in JFA. Therefore, this shows that, AutoML could
examine this unknown space, and find the best possible algorithm in each case.

@@

\hl{przepisac ten szkic bo jezyk sie placzy}

JFA opiera sie na tym ze infomacja jest przekazywana ??????.  Przekazanie odbywa
sie w log(n) krokach. Wiec przeprowadzilismy krotki eksperyment applyujac losowy
szum na wejsciowa masce. Okazalosie sie ze ilosc potrzebnych krokow spadla -
powstaly losowe shortcuty.  Co oznacza ze powinny istniec inne "mutacje"
algorytmow lepsze w pewnych okreslonych przypadkach.  Wiec szukanie najszybszego
algorytmu bedzie nastepujace:

\begin{itemize}
\item Wymyslenie wszystkich mozliwych wariantow JFA
\item Mutacje i zapisanie najlepszych wersji dla danej domeny
\item Ensemblacja algorytmow tak aby wybierac najlepszy variant dla danej domeny
\end{itemize}

>>>>

Based on this research and findings, several efficient GPU-based algorithms
which are either work optimal or time optimal have been proposed including SKW
\cite{schneider2009gpu}, PBA \cite{cao2010parallel}, FastGPU \cite{de2017fast},
Honda's algorithm \cite{honda2017simple} and WTO \cite{manduhu2019work}.
% XXX
The main question that needs to be addressed is whether JFA has potential for
improvement. We found some benefits for specific data by adding random noise and
adjusting the step size in JFA. Therefore, this shows that, AutoML could
examine this unknown space, and find the best possible algorithm in each case.

@@

In this section we outline the general approach that we follow in this work.
When testing a JFA on different domains, we found some performance improvements
by adding random noise and adjusting the step size between flooding rounds. In
order to systematize our research, we adopted the following scheme:

\begin{itemize}
	\item Developing manually new modifications that can be made to the JFA (such
		as using a circle instead of interacting with neighbours in a square
		pattern) and designing them as parameters.
	\item Heuristic search algorithm\footnote{Bayesian optimization
		using Gaussian Processes.} - to examine enormous space of possible variants:
		\begin{itemize}
			\item Implements a new variant from a combination of several
				modifications (mutation).
			\item Tests current variant on various domains and scores the results to update gradient descent.
		\end{itemize}
	\item Knowing the best variant in a specific domain, we can use it in ensemble (when entering the input, ensemble algorithm will decide which algorithm will solve it).
\end{itemize}

%\begin{itemize}
%\item Wymyslenie wszystkich mozliwych wariantow JFA
%\item Mutacje i zapisanie najlepszych wersji dla danej domeny
%\item Ensemblacja algorytmow tak aby wybierac najlepszy variant dla danej domeny
%\end{itemize}

% Come up with new modifications that can be made to the JFA (e.g. instead of communicating with your neighbors in a square shape, use a circle)
